A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

### 2024-12-15 manuscript/manuscript.qmd
added funding statement

[**Short running title**]{.underline}: ...

@@

[**Funding Statement:**]{.underline} This project was supported by ...

>>>>

[**Short running title**]{.underline}: Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

@@

[**Funding Statement:**]{.underline} This project was supported by an FDA BAA contract with contract number 75F40122C00181.
